---
title: "esm206_lab_5"
author: "Dylan Glave"
date: "10/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Objectives: 

- Getting counts for different groups
- Use {lubridate} to parse dates
- Find confidence intervals & do t-tests with t.test()
- Heatmap with geom_tile()
```{r, include=FALSE}
# Attaching Packages

library(tidyverse)
library(here)
library(janitor)

```

```{r}
# Import Lobster Data 

lobster_abundance <- read.csv(here("data", "lobster_abundance.csv"), na = "-99999") %>% 
  clean_names()

```

Use dplyr uncount to expand longer to give any row with "45" lobsters, will now be 45 observations. Removes "count" row and gives each counted lobster its own rown

```{r}
lobster_tidy <- lobster_abundance %>% 
  tidyr::uncount(lobster_count)
```

Yay! Each lobster now has its own row. 1 variable per column, 1 observation per row AND 1 measurement per cell. 

Let's look at df a few different way: 
```{r}

ggplot(data = lobster_tidy, aes( x = site, y = size_mm)) +
  geom_jitter(aes(color = site),
              width = 0.2,
              alpha = .3)

```


```{r}
ggplot(data = lobster_tidy, aes( x = site, y = size_mm)) +
  geom_violin(aes(color = site),
              alpha = .3)
```



```{r}
ggplot(data = lobster_tidy, aes(x = size_mm)) +
geom_histogram(aes(fill = site)) +
facet_wrap(~site, scales = "free")


ggplot(data = lobster_tidy, aes(sample = size_mm)) +
geom_qq(aes(fill = site), 
         size = 0.5) +
facet_wrap(~site, scales = "free")
```


Use {lubridate} package to edit date and time:
Good to specify package, 

I'm going to use mutate() to add new column as an actual date. 

```{r}
lobster_date <- lobster_tidy %>% 
  mutate(
    date_new = lubridate::mdy(date)
  )
```

Parse date_new column to get month and year separated. 

```{r}
lobster_parse_date <- lobster_date %>% 
  mutate(obs_month = lubridate::month(date_new, label = TRUE),
         obs_year = lubridate::year(date_new))
```


Count lobsters by different groupings...

Let's say i want to count the number of lobsters by year and month

```{r}
lobster_yn <- lobster_parse_date %>%
  count(obs_year, obs_month)

lobster_yn

lobster_ysite <- lobster_parse_date %>% 
  count(obs_year, site)

lobster_site <- lobster_parse_date %>% 
  count(site)

# group_by + summarize + n()
lobster_summary <- lobster_parse_date %>% 
  group_by(site) %>% 
  summarize(
    mean_size = mean(size_mm, na.rm = TRUE),
    sd_size = sd(size_mm, na.rm = TRUE),
    sample_n = n())
lobster_summary
```


Confidence Intervals and T-tests

Use the t-test() function to find confidence intervals and perform t-tests

```{r}
ivee_lobsters <- lobster_tidy %>% 
  filter(site == "IVEE") %>% 
  pull(size_mm)

t.test(ivee_lobsters)
```

Two-sample T-test: 
Is there a significant difference between Maples and Mohawk Reef?

```{r}
naples_sample <- lobster_tidy %>% 
  filter(site == "NAPL") %>%
  pull(size_mm)

mohk_sample <- lobster_tidy %>% 
  filter(site == "MOHK") %>% 
  pull(size_mm)

mohk_napl_ttest <- t.test(naples_sample, mohk_sample)
mohk_napl_ttest

```

Mean lobster size differed significantly between Mohawk and Naples Reefs (t(  'r mohk_napl_ttest$parameter'), = 19.849)

Maybe an easier way...

```{r}
lobster_2_sample <- lobster_tidy %>% 
  filter(site %in% c("NAPL", "MOHK"))

ttest_2 <- t.test(size_mm ~ site, data = lobster_2_sample)
ttest_2

```

Make a geom_tile heatmap: 2 discrete variables, x, y axis, color is dependent on fill on density  

```{r}
ggplot(data = lobster_ysite, aes(x = obs_year, y = site)) +
  geom_tile(aes(fill = n))
```

